% Section 4: System Requirements
\section{System Requirements}

This section specifies the system requirements at different levels: domain, product, data, and quality. The requirements have been elicited through the techniques described in Section 3 and are documented using multiple specification techniques to ensure comprehensive coverage and clarity for all stakeholders.

\vspace{0.3cm}

\textbf{Specification Techniques Used:}

The following specification techniques have been employed to document the CookWise system requirements:

\begin{enumerate}
    \item \textbf{Context Diagram} (Section 1.5): Visual representation of the system boundaries and external entities, showing how CookWise interacts with users, stores, and external services.

    \item \textbf{Use Case Diagrams} (Section 4.2): Visual representation of user interactions with the system, showing both the overall system use cases and a detailed view of the core recipe browsing workflow.

    \item \textbf{Feature Requirements} (Textual): Product-level requirements (PR1-PR15) are specified as textual "shall" statements describing specific system capabilities and behaviors.

    \item \textbf{Data Model (Entity-Relationship Diagram)} (Section 4.4): Visual representation of all data entities, their attributes, and relationships using an ERD to ensure database design clarity.

    \item \textbf{Data Dictionary} (Section 4.4): Textual description of all data requirements (DR1-DR4) covering core entities, relationships, data formats, and system configuration.

    \item \textbf{Domain Rules} (Section 4.1): Textual specification of business rules and constraints (DL1-DL6) that define the problem domain and operational boundaries.

    \item \textbf{Quality Requirements Specification} (Section 4.5): Structured specification of non-functional requirements (QR1-QR5) with measurable quality attributes using the QUPER model.
\end{enumerate}

\vspace{0.3cm}

This combination of techniques ensures that requirements are communicated effectively to different stakeholders: visual models for system architects and developers, textual specifications for business stakeholders and testers, and structured quality metrics for project managers and quality assurance teams.

\input{section 4/4_1_domain_requirements}
\input{section 4/4_2_use_cases}
\input{section 4/4_3_functional_requirements}
\input{section 4/4_4_data_requirements}
\input{section 4/4_5_quality_requirements}